---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
# read the raw data into data frame objec rawData
rawData <- read.csv(unz("activity.zip", "activity.csv"))
# filter out NAs
filteredData <- rawData[complete.cases(rawData),]
# Aggregate steps, sum by date and store in q1HistoData
q1HistoData <- aggregate(filteredData$steps, by=list(Date=filteredData$date), FUN=sum)
Q2Data <- aggregate(filteredData$steps, by=list(Interval=filteredData$interval), FUN=mean)

```



## What is mean total number of steps taken per day?

Below is the histogram for sum of steps by Date

```{r, echo=FALSE}
barplot(q1HistoData$x, names.arg=q1HistoData$Date, las=2, main = "Total number of steps taken each day")
```

Mean - total number of steps taken per day : 
```{r}
paste('Mean - total number of steps taken per day : ', mean(q1HistoData$x))

```

Median - total number of steps taken per day: 
```{r}
paste('Median - total number of steps taken per day : ', median(q1HistoData$x))

```


## What is the average daily activity pattern?

```{r, echo=FALSE}
plot(Q2Data, type = 'l', main = 'Average number of steps taken (averaged across all days) versus the 5-minute intervals', xlab='5-minute intervals', ylab='averaged across all days')
```

Below is the calculation that work out the 5-minute interval that, on average, contains the maximum number of steps:

In 5-minute interval
```{r}
paste('Maximum steps interval = ', Q2Data[Q2Data$x == max(Q2Data$x), "Interval"])

```

In equivalent time in the day:
```{r}
maxMinuteInt <- Q2Data[Q2Data$x == max(Q2Data$x), "Interval"]
paste('Maximum stpes interval in Time = ', maxMinuteInt %/% 60, ':' , maxMinuteInt %% 60)
```



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
